# Reproducible Research: Peer Assessment 1 - J Sieber 5/17/14


## Loading and preprocessing the data

Load any librarys.
```{r echo=TRUE}
    library(ggplot2)
```

Load data into variable called act.  Make sure activity.csv is in working directory.

```{r echo=TRUE}
    act<-read.csv("./activity.csv")
    act$date <- strptime(activity.data$date,'%Y-%m-%d')
```

Remove all NAs from data.
```{r echo=TRUE}
    good<-!is.na(act[,1])
    act<-act[good,]
```

## What is mean total number of steps taken per day?

Calculate mean and sum per day
```{r echo=TRUE}
    PerDay<-data.frame(sapply(split(act[,1],act[,2]),sum))
    len<-dim(PerDay)[1]
    names(PerDay)<-c("Sum")
    PerDay$Day<-c(1:len)
    PerDay$Mean<-sapply(split(act[,1],act[,2]),mean)
    PerDay$Median<-sapply(split(act[,1],act[,2]),median)
```

Display histogram of the total number of steps taken each day.
```{r echo=TRUE}

    qplot(Sum, data=PerDay)

```

Display the mean and median steps per day.
```{r echo=TRUE}
    PerDay[,3:4]
```


## What is the average daily activity pattern?
Make a time series plot
```{r plot.interval.avgsteps}
with(act,plot(interval,mean(act$steps,na.rm=TRUE)),xlab="Interval",ylab="Average Number of Steps",type="l",main="Average Number of Steps across all Days by Interval"))
```



## Imputing missing values



## Are there differences in activity patterns between weekdays and weekends?

```{r echo=TRUE}

```



```{r echo=TRUE, fig.width=7, fig.height=6}

```

